---
title: "fourthAttempt.rmd"
author: "isilendil"
date: "2014.08.18."
output: html_document
---

### load train set
```{r}
train <- read.csv("~/Kaggle/Titanic:MachineLearningfromDisaster/titanic/train.csv")
```

### load test set
```{r}
test <- read.csv("~/Kaggle/Titanic:MachineLearningfromDisaster/titanic/test.csv")
```

### combine tow data sets
```{r}
test$Survived <- NA
combi <- rbind(train, test)
```

### cast name column, which encoded as factor, back into string
```{r}
combi$Name <- as.character(combi$Name)
combi$Name[1]
```

### break apart a string
```{r}
strsplit(combi$Name[1], split = '[,.]')
strsplit(combi$Name[1], split = '[,.]')[[1]]
strsplit(combi$Name[1], split = '[,.]')[[1]][2]
combi$Title <- sapply(combi$Name, FUN = function(x) { strsplit(x, split='[,.]')[[1]][2]})
combi$Title <- sub(' ', '', combi$Title)
```

### look at the new variable
```{r}
table(combi$Title)
```

### combine some unusual titles into a single catetory
```{r}
combi$Title[combi$Title %in% c('Mme', 'Mlle')] <- 'Mlle'
combi$Title[combi$Title %in% c('Capt', 'Don', 'Major', 'Sir')] <- 'Sir'
combi$Title[combi$Title %in% c('Dona', 'Lady', 'the Countess', 'Jonkheer')] <- 'Lady'
combi$Title <- factor(combi$Title)
```

### create a new variable named FamilySize
```{r}
combi$FamilySize <- combi$SibSp + combi$Parch + 1
```

### new variable called Surname 
```{r}
combi$Surname <- sapply(combi$Name, FUN = function(x) { strsplit(x, split='[,.]')[[1]][1]})
```

### new variable called FamilyID
```{r}
combi$FamilyID <- paste(as.character(combi$FamilySize), combi$Surname, sep = "")
```

single people should not have the same FamilyID
```{r}
combi$FamilyID[combi$FamilySize <= 2] <- 'Small'
```

look at the new variable
```{r}
table(combi$FamilyID)
```

store the table
```{r}
famIDs <- data.frame(table(combi$FamilyID))
```

adjust the FamilyID column
```{r}
famIDs <- famIDs[famIDs$Freq <= 2, ]
combi$FamilyID[combi$FamilyID %in% famIDs$Var1] <- 'Small'
combi$FamilyID <- factor(combi$FamilyID)
```

### split the train set and test set back into their original states
```{r}
train <- combi[1:dim(train)[1], ]
test <- combi[(dim(train)[1]+1):dim(combi)[1], ]
```

### new model
```{r}
library(rpart)
fit <- rpart(Survived ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + FamilySize + FamilyID, data = train, method = "class")
```

load some packages to draw the decision tree
```{r}
library(rattle)
library(rpart.plot)
library(RColorBrewer)
```

render the figure
```{r}
fancyRpartPlot(fit)
```

generate the predicting result
```{r}
Prediction <- predict(fit, test, type = "class")
submit <- data.frame(PassengerId = test$PassengerId, Survived = Prediction)
write.csv(submit, file = "fourthAttempt.csv", row.names = FALSE)
```









