---
title: "secondAttempt"
author: "isilendil"
date: "2014.08.16"
output: pdf_document
---

### load train set
```{r}
train <- read.csv("~/Kaggle/Titanic:MachineLearningfromDisaster/titanic/train.csv")
```

### load test set
```{r}
test <- read.csv("~/Kaggle/Titanic:MachineLearningfromDisaster/titanic/test.csv")
```

### summary results
```{r}
table(train$Sex)
prop.table(table(train$Sex))
```

```{r}
table(train$Sex, train$Survived)
prop.table(table(train$Sex, train$Survived))
```

### proportions in the 1st dimension
```{r}
table(train$Sex, train$Survived)
prop.table(table(train$Sex, train$Survived), 1)
```

### predict according to the gender
test$Survived <- 0
test$Survived[test$Sex == "female"] <- 1

### summary of ages
```{r}
summary(train$Age)
```

### create a new variable to indicate whether the passenger is a child(< 18)
```{r}
train$Child <- 0
train$Child[train$Age < 18] <- 1
```

### the number of survivors in different groups
```{r}
aggregate(Survived ~ Child + Sex, data = train, FUN = sum)
```

### the number of passengers in different groups
```{r}
aggregate(Survived ~ Child + Sex, data = train, FUN = length)
```

### the proportion of survivors in different groups
```{r}
aggregate(Survived ~ Child + Sex, data = train, FUN = function(x) { sum(x) / length(x) })
```

### summary of the fare of tickets
```{r}
summary(train$Fare)
```

### create a new variable to hash the fare to different intervals
```{r}
train$Fare2 <- "30+"
train$Fare2[train$Fare < 30 & train$Fare >= 20] <- "20-30"
train$Fare2[train$Fare < 20 & train$Fare >= 10] <- "10-20"
train$Fare2[train$Fare < 10] <- "<10"
```

### aggregate result about Survived related to Fare2, Sex and Pclass
```{r}
aggregate(Survived ~ Fare2 + Pclass + Sex, data = train, FUN = function(x) { sum(x) / length(x) })
```

### a new prediction
```{r}
test$Survived <- 0
test$Survived[test$Sex == "female"] <- 1
test$Survived[test$Sex == "female" & test$Pclass == 3 & test$Fare >= 20] <- 0
```

###generate result
```{r}
submit <- data.frame(PassengerId = test$PassengerId, Survived = test$Survived)
write.csv(submit, file = "/home/yanyg/Kaggle/Titanic:MachineLearningfromDisaster/titanic/secondAttempt.csv", row.names = FALSE)
```
