---
title: "fifthAttempt"
author: "isilendil"
date: "2014.08.19"
output: html_document
---

### load train set
```{r}
train <- read.csv("~/Kaggle/Titanic:MachineLearningfromDisaster/titanic/data/train.csv")
```

### load test set
```{r}
test <- read.csv("~/Kaggle/Titanic:MachineLearningfromDisaster/titanic/data/test.csv")
```

### combine tow data sets
```{r}
test$Survived <- NA
combi <- rbind(train, test)
```

### cast name column, which encoded as factor, back into string
```{r}
combi$Name <- as.character(combi$Name)
combi$Name[1]
```

### break apart a string
```{r}
strsplit(combi$Name[1], split = '[,.]')
strsplit(combi$Name[1], split = '[,.]')[[1]]
strsplit(combi$Name[1], split = '[,.]')[[1]][2]
combi$Title <- sapply(combi$Name, FUN = function(x) { strsplit(x, split='[,.]')[[1]][2]})
combi$Title <- sub(' ', '', combi$Title)
```

### look at the new variable
```{r}
table(combi$Title)
```

### combine some unusual titles into a single catetory
```{r}
combi$Title[combi$Title %in% c('Mme')] <- 'Mrs'
combi$Title[combi$Title %in% c('Mlle')] <- 'Ms'
combi$Title[combi$Title %in% c('Col', 'Capt', 'Don', 'Major', 'Sir')] <- 'Sir'
combi$Title[combi$Title %in% c('Dona', 'Lady', 'the Countess', 'Jonkheer')] <- 'Lady'
combi$Title <- factor(combi$Title)
```

### create a new variable named FamilySize
```{r}
combi$FamilySize <- combi$SibSp + combi$Parch + 1
```

### new variable called Surname 
```{r}
combi$Surname <- sapply(combi$Name, FUN = function(x) { strsplit(x, split='[,.]')[[1]][1]})
```

### new variable called FamilyID
```{r}
combi$FamilyID <- paste(as.character(combi$FamilySize), combi$Surname, sep = "")
```

single people should not have the same FamilyID
```{r}
combi$FamilyID[combi$FamilySize <= 2] <- 'Small'
```

look at the new variable
```{r}
table(combi$FamilyID)
```

store the table
```{r}
famIDs <- data.frame(table(combi$FamilyID))
```

adjust the FamilyID column
```{r}
famIDs <- famIDs[famIDs$Freq <= 2, ]
combi$FamilyID[combi$FamilyID %in% famIDs$Var1] <- 'Small'
combi$FamilyID <- factor(combi$FamilyID)
```


### sample function test
```{r}
sample(1:10, replace = TRUE)
```

summary of ages
```{r}
summary(combi$Age)
```

### a model to predict ages labeled NA
```{r}
library(rpart)
Agefit <- rpart(Age ~ Pclass + Sex + SibSp + Parch + Fare + Embarked + Title + FamilySize, data = combi[!is.na(combi$Age),], method = "anova")
combi$Age[is.na(combi$Age)] <- predict(Agefit, combi[is.na(combi$Age), ])
```

load some packages to draw the decision tree
```{r}
library(rattle)
library(rpart.plot)
library(RColorBrewer)
```

render the figure
```{r}
fancyRpartPlot(Agefit)
```

### preprocessing 
```{r}
summary(combi)
```

Embarked and Fare have problems.

deal with Embarked
```{r}
summary(combi$Embarked)
which(combi$Embarked == '')
combi$Embarked[which(combi$Embarked == '')] = "S"
combi$Embarked <- factor(combi$Embarked)
```

deal with Fare
```{r}
summary(combi$Fare)
which(is.na(combi$Fare))
combi$Fare[which(is.na(combi$Fare))] <- median(combi$Fare, na.rm = TRUE)
```

deal with FamilyID which has too many factors to satisfy the request of Random Forests in R.
```{r}
combi$FamilyID2 <- combi$FamilyID
combi$FamilyID2 <- as.character(combi$FamilyID2)
combi$FamilyID2[combi$FamilySize <= 3] <- 'Small'
combi$FamilyID2 <- factor(combi$FamilyID2)
```

### split the train set and test set back into their original states
```{r}
train <- combi[1:dim(train)[1], ]
test <- combi[(dim(train)[1]+1):dim(combi)[1], ]
```

### random forests model
```{r}
library(randomForest)
set.seed(415)
fit <- randomForest(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + FamilySize + FamilyID2, data = train, importance = TRUE, ntree = 2000)
```

look at what variables were important
```{r}
varImpPlot(fit)
```

generate predicting result
```{r}
Prediction <- predict(fit, test)
submit <- data.frame(PassengerId = test$PassengerId, Survived = Prediction)
write.csv(submit, file = "/home/yanyg/Kaggle/Titanic:MachineLearningfromDisaster/titanic/sixthAttempt/sixthAttempt1.csv", row.names = FALSE)
```

### new model using a forest of conditional inference trees
```{r}
library(party)
set.seed(415)
fit <- cforest(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + FamilySize + FamilyID, data = train, controls = cforest_unbiased(ntree=2000, mtry=3))
```

generate predicting result
```{r}
Prediction <- predict(fit, test, OOB = TRUE, type = "response")
submit <- data.frame(PassengerId = test$PassengerId, Survived = Prediction)
write.csv(submit, file = "/home/yanyg/Kaggle/Titanic:MachineLearningfromDisaster/titanic/sixthAttempt/sixthAttempt2.csv", row.names = FALSE)
```

### diff two results
```{r}
result0 <- read.csv("~/Kaggle/Titanic:MachineLearningfromDisaster/titanic/fifthAttempt/fifthAttempt2.csv")
result1 <- submit
resultCombi <- rbind(result0, result1)
resultCombi$Survived <- as.integer(resultCombi$Survived)
result0 <- resultCombi[1:nrow(result0), ]
result1 <- resultCombi[(nrow(result0)+1):nrow(resultCombi), ]
result0$Survived - result1$Survived
```










